---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# H2o Helper

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/h2ohelper)](https://cran.r-project.org/package=h2ohelper)
[![Travis-CI Build Status](https://travis-ci.org/seabbs/h2ohelper.svg?branch=master)](https://travis-ci.org/seabbs/h2ohelper)
[![Coverage Status](https://img.shields.io/codecov/c/github/seabbs/h2ohelper/master.svg)](https://codecov.io/github/seabbs/h2ohelper?branch=master)

This package aims to provide utility, quality of life, and presentation improving wrappers around the functionality provided by the [h2o](http://docs.h2o.ai/) R package.

## Installation

You can install h2ohelper from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("seabbs/h2ohelper")
```

## Docker

This package has been developed in docker based on the `rocker/tidyverse` image, to access the  development environment enter the following at the command line (with an active docker daemon running),

```{bash, eval = FALSE}
docker pull seabbs/h2ohelper
docker run -d -p 8787:8787 -p 54321:54321 -e USER=seabbs -e PASSWORD=h2ohelper --name h2ohelper seabbs/h2ohelper
```

The rstudio client can be accessed on port `8787` at `localhost` (or your machines ip).
